|

### 2024-07-10 doc/paper_mine.qmd
Correct data pathing in paper.qmd and according comment in README

import pandas as pd
import numpy as np
import os

# Paths to data files
static_data_path = '/Users/melissam/Documents/GitHub/arg_trr266/data/external/wscp_static.txt' 
panel_data_path = '/Users/melissam/Documents/GitHub/arg_trr266/data/external/wscp_panel.xlsx'

# Check if files exist
if not os.path.exists(static_data_path):
    raise FileNotFoundError(f"{static_data_path} does not exist.")
if not os.path.exists(panel_data_path):
    raise FileNotFoundError(f"{panel_data_path} does not exist.")

# Load the data from Worldscope files into pandas DataFrames
static_data = pd.read_csv(static_data_path, delimiter='\t')  # use '\t' due to tab-separation in the static file
panel_data = pd.read_excel(panel_data_path)

>>>>

import pandas as pd
import numpy as np
import os
import yaml

# Function to get the path of the current file
def get_current_path():
    try:
        return os.path.dirname(os.path.abspath(__file__))
    except NameError:
        return os.getcwd()

# Define the relative path to the configuration file
config_path = os.path.join(get_current_path(), '..', 'config', 'config.yaml')
with open(config_path, 'r') as file:
    config = yaml.safe_load(file)

# Extract paths from the config file
STATIC_DATA_PATH = os.path.join(get_current_path(), '..', config['data_paths']['static_data'])
PANEL_DATA_PATH = os.path.join(get_current_path(), '..', config['data_paths']['panel_data'])

# Check if files exist
if not os.path.exists(STATIC_DATA_PATH):
    raise FileNotFoundError(f"{STATIC_DATA_PATH} does not exist.")
if not os.path.exists(PANEL_DATA_PATH):
    raise FileNotFoundError(f"{PANEL_DATA_PATH} does not exist.")

# Load the data from Worldscope files into pandas DataFrames
static_data = pd.read_csv(STATIC_DATA_PATH, delimiter='\t')  # use '\t' due to tab-separation in the static file
panel_data = pd.read_excel(PANEL_DATA_PATH)
